Characterizing Signal Loss in the 21\,cm Reionization Power Spectrum: \\A Revised Study of PAPER-64

### 2018-11-01 PAPER.tex
small syntax edit

\documentclass[preprint2,numberedappendix,tighten]{aastex6}  % USE THIS TO MAKE BIB, THEN FORMAT USING EMULATEAPJ
%\documentclass[twocolumn,numberedappendix]{emulateapj}
\shorttitle{Characterizing Signal Loss in the 21\,cm Reionization Power Spectrum}
\shortauthors{Cheng et al.}

@@

In addition to the first tentative detection of our \textit{Cosmic Dawn} (pre-reionization era) made by the Experiment to Detect the Global EoR Signature (EDGES; \citealt{bowman_et_al2018}; \citealt{bowman2010}), there are several radio telescope experiments that have succeeded in using 
the 21\,cm signal from hydrogen to place constraints on the brightness of the signal. Examples of experiments investigating the 
mean brightness temperature of the 21\,cm signal relative to the CMB are the Large Aperture Experiment to Detect the Dark Ages (LEDA; \citealt{bernardi_et_al2016}), the 
Dark Ages Radio Explorer (DARE; \citealt{burns2012}), the Sonda Cosmol\'ogica de las Islas para la Detecci\'on de 
Hidr\'ogeno NeutroSciHi (SCI-HI; \citealt{voytek2014}), the Broadband Instrument for Global HydrOgen ReioNisation Signal 
(BIGHORNS; \citealt{sokolowski2015}), and the Shaped Antenna measurement of the background RAdio Spectrum (SARAS; 
\citealt{patra2015}). Radio interferometers which seek to measure statistical power spectra include the Giant Metre-wave 
Radio Telescope (GMRT; \citealt{paciga_et_al2013}), the LOw Frequency ARray (LOFAR; \citealt{van_haarlem_et_al2013}), 
the Murchison Widefield Array (MWA; \citealt{tingay_et_al2013}), the 21 Centimeter Array (21CMA; 
\citealt{peterson_et_al2004}; \citealt{wu2009}), the Square Kilometre Array (SKA; \citealt{koopmans_et_al2015}), and PAPER (\citealt{parsons_et_al2010}). The Hydrogen Epoch of 
Reionization Array (HERA), which is currently being built, is a next-generation instrument that aims to combine lessons 
learned from previous experiments and has a forecasted sensitivity capable of a high-significance power spectrum 
detection with an eventual $350$ elements using current analysis techniques (\citealt{pober_et_al2014}; \citealt{liu_parsons_2016}; \citealt{dillon_parsons2016}; \citealt{deboer_et_al2017}).

@@

This paper is organized into three main sections. In Section \ref{sec:SiglossOverview} we use toy models to develop intuition about signal loss, its origin, and its subtleties. In Section \ref{sec:CaseStudy}, we present a case study using data from the PAPER-64 array, highlighting key changes from the signal loss methods used in the published result in \citet{ali_et_al2015}, henceforth known as \citetalias{ali_et_al2015}, which previously underestimated loss. In Section \ref{sec:OtherErrors}, we summarize additional lessons learned since \citetalias{ali_et_al2015} that have shaped our revised analysis. Finally, we conclude in Section \ref{sec:Con}.

@@

We begin with an overview of the quadratic estimator (QE) formalism used for power spectrum estimation. The goal of power spectrum analysis is to produce an unbiased estimator of the EoR power spectrum in the presence of both noise and foreground emission. Prior to power spectrum estimation, the data will often have been prepared to have minimal foregrounds by some method of subtraction, so this foreground emission may appear either directly (because it was not subtracted) or as a residual of some subtraction process not in the power spectrum domain. If an accurate estimate of the total covariance of the data is known, including both the desired signal and any contaminants, then the ``optimal quadratic estimator'' formalism provides a method of producing a minimum variance, unbiased estimator of the desired signal, as shown in 
% JEA - I cut this b/c I wanted to step back and explain a bit more clearly what we were actually hoping for 
%Driven by the need to mitigate foreground bias, PAPER's previous analyses use a weighting method that aims to down-weight foregrounds. This weighting is applied to data, which is then propagated into a final estimator using the power spectrum estimation technique of quadratic estimators (QE) as done in 
\citet{liu_tegmark2011}, \citet{dillon_et_al2013a}, \citet{liu_et_al2014a}, \citet{liu_et_al2014b}, \citet{trott_et_al2012}, \citet{dillon_et_al2014}, \citet{dillon_et_al2015}, \citet{switzer_et_al2015}, and \citet{trott_et_al2016}. 
%Before showing how signal loss can arise when using different weighting matrices, we first summarize QE as performed in the PAPER analysis.

@@

\bibliographystyle{apj}
\bibliography{refs}

>>>>

\documentclass[preprint2,numberedappendix,tighten]{aastex6}  % USE THIS TO MAKE BIB, THEN FORMAT USING EMULATEAPJ
%\documentclass[twocolumn,numberedappendix]{emulateapj}
%\documentclass[preprint2]{emulateapj}
\shorttitle{Characterizing Signal Loss in the 21\,cm Reionization Power Spectrum}
\shortauthors{Cheng et al.}

@@

In addition to the first tentative detection of our \textit{Cosmic Dawn} (pre-reionization era) made by the Experiment to Detect the Global EoR Signature (EDGES; \citealt{bowman_et_al2018}; \citealt{bowman2010}), there are several radio telescope experiments that have succeeded in using 
the 21\,cm signal from hydrogen to place constraints on the brightness of the signal. Examples of experiments investigating the 
mean brightness temperature of the 21\,cm signal relative to the CMB are the Large Aperture Experiment to Detect the Dark Ages (LEDA; \citealt{bernardi_et_al2016}), the 
Dark Ages Radio Explorer (DARE; \citealt{burns2012}), the Sonda Cosmol\'ogica de las Islas para la Detecci\'on de 
Hidr\'ogeno NeutroSciHi (SCI-HI; \citealt{voytek2014}), the Broadband Instrument for Global HydrOgen ReioNisation Signal 
(BIGHORNS; \citealt{sokolowski2015}), and the Shaped Antenna measurement of the background RAdio Spectrum (SARAS; 
\citealt{patra2015}). Radio interferometers which seek to measure statistical power spectra include the Giant Metre-wave 
Radio Telescope (GMRT; \citealt{Paciga2013}), the LOw Frequency ARray (LOFAR; \citealt{van_haarlem_et_al2013}), 
the Murchison Widefield Array (MWA; \citealt{tingay_et_al2013}), the 21 Centimeter Array (21CMA; 
\citealt{peterson_et_al2004}; \citealt{wu2009}), the Square Kilometre Array (SKA; \citealt{koopmans_et_al2015}), and PAPER (\citealt{parsons_et_al2010}). The Hydrogen Epoch of 
Reionization Array (HERA), which is currently being built, is a next-generation instrument that aims to combine lessons 
learned from previous experiments and has a forecasted sensitivity capable of a high-significance power spectrum 
detection with an eventual $350$ elements using current analysis techniques (\citealt{pober_et_al2014}; \citealt{liu_parsons_2016}; \citealt{dillon_parsons2016}; \citealt{deboer_et_al2017}).

@@

This paper is organized into four main sections. In Section \ref{sec:SiglossOverview} we use toy models to develop intuition about signal loss, its origin, and its subtleties. In Section \ref{sec:CaseStudy}, we present a case study using data from the PAPER-64 array, highlighting key changes from the signal loss methods used in the published result in \citet{ali_et_al2015}, henceforth known as \citetalias{ali_et_al2015}, which previously underestimated loss. In Section \ref{sec:OtherErrors}, we summarize additional lessons learned since \citetalias{ali_et_al2015} that have shaped our revised analysis. Finally, we conclude in Section \ref{sec:Con}.

@@

We begin with an overview of the quadratic estimator (QE) formalism used for power spectrum estimation. The goal of power spectrum analysis is to produce an unbiased estimator of the EoR power spectrum in the presence of both noise and foreground emission. Prior to power spectrum estimation, the data will often have been prepared to have minimal foregrounds by some method of subtraction, so this foreground emission may appear either directly (because it was not subtracted) or as a residual of some subtraction process not in the power spectrum domain. If an accurate estimate of the total covariance of the data is known, including both the desired signal and any contaminants, then the ``optimal quadratic estimator'' formalism provides a method of producing a minimum variance, unbiased estimator of the desired signal, as shown in 
% JEA - I cut this b/c I wanted to step back and explain a bit more clearly what we were actually hoping for 
%Driven by the need to mitigate foreground bias, PAPER's previous analyses use a weighting method that aims to down-weight foregrounds. This weighting is applied to data, which is then propagated into a final estimator using the power spectrum estimation technique of quadratic estimators (QE) as done in 
\citet{liu_tegmark2011}, \citet{trott_et_al2012}, \citet{dillon_et_al2013a}, \citet{liu_et_al2014a}, \citet{liu_et_al2014b}, \citet{dillon_et_al2014}, \citet{dillon_et_al2015}, \citet{switzer_et_al2015}, and \citet{trott_et_al2016}. 
%Before showing how signal loss can arise when using different weighting matrices, we first summarize QE as performed in the PAPER analysis.

@@

%\bibliographystyle{apj}
\bibliography{refs}
